---
title: "R Project 1 - Hello R"
author: "Gerardo Hernandez"
date: "Due Fed 3rd"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

It has 1846 rows with 0 columns. It has 3 variables which are  dataset, x: x-values, and y: y-values.

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Lets plot the data for the starset and plot the graph:


```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
```{r cor-star}
star_data %>%
summarize(r = cor(x,y))
```


### Exercise 4

Lets plot the data is the circle and plot the graph:


```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
summarize(r = cor(x,y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
